Postural changes mediate children's visual access to social information

### 2018-01-15 writeup-cogsci-copy/cogsci2018.Rmd
wrist and hand

original_candidates <- read_csv("../data/ground_truth/gold_set_candidates2.csv") %>%
  arrange(video, frame)

ground_truth_data <- read_csv("../data/ground_truth/ground_truth3.csv") %>%
  select(-angle) %>%
  arrange(video, frame) %>%
  cbind(original_candidates %>%
          select(sample_type))

@@

@@

render_table(mtcnn_results, "MTCNN")
render_table(openpose_results, "OpenPose")

>>>>

ground_truth_data <- read_csv("../data/ground_truth/ground_truth3.csv") %>%
  select(-angle) %>%
  arrange(video, frame) %>%
  cbind(read_csv("../data/ground_truth/gold_set_candidates2.csv") %>%
          arrange(video, frame) %>%
          select(sample_type))

data_openpose_wrists <- read_csv("../data/final_output/openpose_results_truncated_2.csv") %>%
  distinct(name, frame, .keep_all = TRUE) %>%
  mutate(is_hand = ifelse(LWrist_conf != 0 | RWrist_conf != 0, "True", "False")) %>%
  select(group, name, frame, is_hand) %>%
  rename(video = name)

data_openpose_hands <- read_csv("../data/final_output/openpose_results_with_detail_hands.csv") %>%
  distinct(name, frame, .keep_all = TRUE) %>%
  mutate(video = name) %>%
  distinct(video,frame,.keep_all=TRUE)  %>%
  select(group, video,frame,ends_with("conf")) %>%
  mutate(confLeft=rowSums(.[grep("hand_left", names(.))])/21)  %>%
  mutate(confRight=rowSums(.[grep("hand_right", names(.))])/21)  %>%
  mutate(is_hand = ifelse(confRight>=.5 | confLeft>=.5, "True", "False"))

ground_truth_data_hands <- read_csv("../data/ground_truth/ground_truth_hands.csv") %>%
  rename(is_hand = is_face) %>%
  select(-angle) %>%
  arrange(video, frame) %>%
  cbind(read_csv("../data/ground_truth/gold_set_hand_candidates.csv") %>%
          arrange(video, frame) %>%
          select(sample_type))

@@

openpose_wrist_results <- data_openpose_wrists %>%
  rename(detector_is_hand = is_hand) %>%
  inner_join(ground_truth_data_hands, by = c("group", "video", "frame")) %>%
  rowwise() %>%
  mutate(result = evaluate(is_hand, detector_is_hand))

openpose_hand_results <- data_openpose_hands %>%
  rename(detector_is_hand = is_hand) %>%
  inner_join(ground_truth_data_hands, by = c("group", "video", "frame")) %>%
  rowwise() %>%
  mutate(result = evaluate(is_hand, detector_is_hand))

@@

render_table(mtcnn_results, "MTCNN")
render_table(openpose_results, "OpenPose")
render_table(openpose_wrist_results, "OpenPose Wrist")
render_table(openpose_hand_results, "OpenPose Hand")

### 2018-01-15 writeup-cogsci-copy/cogsci2018.tex
wrist and hand

Children are remarkably skilled language learners, connecting arbitrary
labels (``cup'') with specific visual concepts at a rapid pace through
the first two years of life. However, children do not learn words in a
vacuum but in a rich social environment, where social cues provided by
speakers (e.g., eye-gaze) provide strong scaffolding for this learning
process. Indeed, children's ability to effectively process these social
cues may be a key factor in their early language development. For
example,in a longitudinal study, children's level of joint engagement
with their mother was found to predict both their receptive and
productive vocabularies (Carpenter, Nagell, \& Tomasello (1998)). More
recently, 10 month-olds who follow an adult's gaze in an experimental
context have larger vocabularies at 18 months (R. Brooks \& Meltzoff
(2005)) and throughout the second year of life (Rechele Brooks \&
Meltzoff (2008)).

@@

Recent work has begun to use egocentric, head-mounted cameras to
document the visual experiences of infants and children --- which even
for walking children are radically different than the adult perspective
(and not easily predicted by our own adult intuitions; J. Franchak et
al. (2011), Yoshida \& Smith (2008); Clerkin, Hart, Rehg, Yu, \& Smith
(2017)). Children's views tend to be restricted and to be dominated by
objects and hands much more than that of adults (Yoshida \& Smith,
2008), and both computational and empirical work suggest that this
restricted viewpoint may be more effective for learning what objects and
their labels than the comparable adult perspective (D. Yurovsky, Smith,
\& Yu, in press, Bambach, Crandall, Smith, \& Yu (2017)). Further,
recent work also suggests dramatic changes in the child's perspective
over the first two years of life, as views transition from primarily
containing close up view of faces to capturing views of hands paired
with the objects they are acting on (Fausey, Jayaraman, \& Smith, 2016).

Here, we directly ask whether the postural changes that infants'
experience as they reach their first birthday change the availability of
the social information relevant for word learning. To do so, we recorded
the visual experience of a group of infants and children using
head-mounted cameras during a brief laboratory free-play session;
children's posture and their orientation to their caregiver were also
recorded from a third-person perspective and hand-annotated. We
capitalize on recent improvements in computer vision algorithms (K.
Zhang, Zhang, Li, \& Qiao (2016), Cao, Simon, Wei, \& Sheikh (2017))
that allow the automated detection of both faces and hands, and we
analyze the frequency of both faces and hands in the child's visual
environment.

@@

\begin{table}[H]
\centering
\begin{tabular}{rrrr}
  \hline
 & P & R & F \\ 
  \hline
1 & 0.84 & 1.00 & 0.91 \\ 
   \hline
\end{tabular}
\caption{MTCNN High Density Sample} 
\end{table}\begin{table}[H]
\centering
\begin{tabular}{rrrr}
  \hline
 & P & R & F \\ 
  \hline
1 & 0.95 & 0.75 & 0.84 \\ 
   \hline
\end{tabular}
\caption{MTCNN Random Sample} 
\end{table}\begin{table}[H]
\centering
\begin{tabular}{rrrr}
  \hline
 & P & R & F \\ 
  \hline
1 & 0.99 & 0.87 & 0.93 \\ 
   \hline
\end{tabular}
\caption{OpenPose High Density Sample} 
\end{table}\begin{table}[H]
\centering
\begin{tabular}{rrrr}
  \hline
 & P & R & F \\ 
  \hline
1 & 0.71 & 0.92 & 0.80 \\ 
   \hline
\end{tabular}
\caption{OpenPose Random Sample} 
\end{table}

@@

>>>>

Children are remarkably skilled language learners, connecting arbitrary
labels (``cup'') with specific visual concepts at a rapid pace through
the first two years of life. However, children do not learn words in a
vacuum but in a rich social environment, where social cues provided by
speakers (e.g., eye-gaze) provide strong scaffolding for this learning
process. Indeed, children's ability to effectively process these social
cues may be a key factor in their early language development. For
example,in a longitudinal study, children's level of joint engagement
with their mother was found to predict both their receptive and
productive vocabularies (Carpenter, Nagell, \& Tomasello, 1998). More
recently, 10 month-olds who follow an adult's gaze in an experimental
context have larger vocabularies at 18 months (R. Brooks \& Meltzoff,
2005) and throughout the second year of life {]}Rechele Brooks \&
Meltzoff (2008){]}.

@@

Recent work has begun to use egocentric, head-mounted cameras to
document the visual experiences of infants and children --- which even
for walking children are radically different than the adult perspective
(and not easily predicted by our own adult intuitions; (Clerkin, Hart,
Rehg, Yu, \& Smith, 2017; J. Franchak et al., 2011, Yoshida \& Smith
(2008)) ). Children's views tend to be restricted and to be dominated by
objects and hands much more than that of adults (Yoshida \& Smith,
2008), and both computational and empirical work suggest that this
restricted viewpoint may be more effective for learning what objects and
their labels than the comparable adult perspective (Bambach, Crandall,
Smith, \& Yu, 2017; D. Yurovsky, Smith, \& Yu, in press). Further,
recent work also suggests dramatic changes in the child's perspective
over the first two years of life, as views transition from primarily
containing close up view of faces to capturing views of hands paired
with the objects they are acting on (Fausey, Jayaraman, \& Smith, 2016).

Here, we directly ask whether the postural changes that infants'
experience as they reach their first birthday change the availability of
the social information relevant for word learning. To do so, we recorded
the visual experience of a group of infants and children using
head-mounted cameras during a brief laboratory free-play session;
children's posture and their orientation to their caregiver were also
recorded from a third-person perspective and hand-annotated. We
capitalize on recent improvements in computer vision algorithms (K.
Zhang, Zhang, Li, \& Qiao, 2016, Cao, Simon, Wei, \& Sheikh (2017)) that
allow the automated detection of both faces and hands, and we analyze
the frequency of both faces and hands in the child's visual environment.

@@

\begin{table}[H]
\centering
\begin{tabular}{rrrr}
  \hline
 & P & R & F \\ 
  \hline
1 & 0.84 & 1.00 & 0.91 \\ 
   \hline
\end{tabular}
\caption{MTCNN High Density Sample} 
\end{table}\begin{table}[H]
\centering
\begin{tabular}{rrrr}
  \hline
 & P & R & F \\ 
  \hline
1 & 0.95 & 0.75 & 0.84 \\ 
   \hline
\end{tabular}
\caption{MTCNN Random Sample} 
\end{table}\begin{table}[H]
\centering
\begin{tabular}{rrrr}
  \hline
 & P & R & F \\ 
  \hline
1 & 0.99 & 0.87 & 0.93 \\ 
   \hline
\end{tabular}
\caption{OpenPose High Density Sample} 
\end{table}\begin{table}[H]
\centering
\begin{tabular}{rrrr}
  \hline
 & P & R & F \\ 
  \hline
1 & 0.71 & 0.92 & 0.80 \\ 
   \hline
\end{tabular}
\caption{OpenPose Random Sample} 
\end{table}\begin{table}[H]
\centering
\begin{tabular}{rrrr}
  \hline
 & P & R & F \\ 
  \hline
1 & 0.65 & 0.85 & 0.74 \\ 
   \hline
\end{tabular}
\caption{OpenPose Wrist High Density Sample} 
\end{table}\begin{table}[H]
\centering
\begin{tabular}{rrrr}
  \hline
 & P & R & F \\ 
  \hline
1 & 0.32 & 0.13 & 0.19 \\ 
   \hline
\end{tabular}
\caption{OpenPose Wrist Random Sample} 
\end{table}\begin{table}[H]
\centering
\begin{tabular}{rrrr}
  \hline
 & P & R & F \\ 
  \hline
1 & 1.00 & 0.21 & 0.35 \\ 
   \hline
\end{tabular}
\caption{OpenPose Hand High Density Sample} 
\end{table}\begin{table}[H]
\centering
\begin{tabular}{rrrr}
  \hline
 & P & R & F \\ 
  \hline
1 & 1.00 & 0.04 & 0.09 \\ 
   \hline
\end{tabular}
\caption{OpenPose Hand Random Sample} 
\end{table}

@@

\hypertarget{ref-iverson2010}{}
Iverson, J. M. (2010). Developing language in a developing body: The
relationship between motor development and language development.
\emph{Journal of Child Language}, \emph{37}(2), 229--261.
